Phylogenetic adaptions to urban living in Australian birds

### 2018-04-07 ms.Rmd
differences between knit to html and knit to tufte_html_2. Can't figure out how to knit to pdf

---
title: "Phylogenetic adaptions to urban living in Australian birds"
author: Corey T. Callaghan, John Wilshire, XXXX, XXXX, Richard T. Kingsford, William K. Cornwell
date: ""
output:
  html_document:
    df_print: paged
    toc: no
  bookdown::word_document2: null
  pdf_document: null
  bookdown::tufte_html2:
    number_sections: no
    toc: no
fontsize: 12pt
link-citations: no
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/global-ecology-and-biogeography.csl
bibliography: references.bib
---

>>>>

---
title: "Phylogenetic adaptions to urban living in Australian birds"
author: Corey T. Callaghan, John Wilshire, XXXX, XXXX, Richard T. Kingsford, William K. Cornwell
date: ""
output:
  bookdown::tufte_html2:
    number_sections: no
    toc: no
  bookdown::word_document2: null
  pdf_document: null
  html_document:
    df_print: paged
    toc: no
fontsize: 12pt
link-citations: no
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/global-ecology-and-biogeography.csl
bibliography: references.bib
---
